---
title: "A UN Report on the relationship between"
author: "Takao"
date: "5/25/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
```
This is report was prepared to the attention of the United Nations. it analysis the realtinship between a coiuntry's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country's ecomic strength or weakness may be relted to its public health status and impact on climate pollution. We

```{r}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```
```{r gdp_lifeexp_1997}
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y=lifeExp, color = continent, size=pop/100000) +
  geom_point() +
  labs(x = "GDP Per Capita", y= "life expectancy", title ="I'm proud of myself",
  size="Population(in millions)")
```

```{r, include=FALSE}
# this piece of code count the number of countries
nCountries <- gapminder_1997 %>%  select(country) %>%  n_distinct()
minGDP <- gapminder_1997 %>%  summarise(round(min(gdpPercap))) %>% 
pull()
maxGDP <- gapminder_1997 %>%  summarise(round(max(gdpPercap))) %>% 
pull()
```

The above plot shows the relationship between GDP per capta and life expectancy
for a total of 'r nCountries' countries. For this set of countries, ecnomic wealth ranged from a minimum of USD 'r minGDP' to a maximum of USD 'r maxGDP' per capita.

| HEADER 1 | HEADER 2 |
| -------- | -------- |
| row 1, column 1 | row 1, column 2|
| row 2, column 1 | row 2, column 2|

```{r kable_table}
library(knitr)
gapminder_1997 %>% 
  filter(continent == "Oceania") %>% 
  kable()
```

